Web Processing - Standardised GIS Analyses for Cable Route Planning

### 2023-01-09 paper/paper-CableRoute.tex
updated paper:
added new ideas for next steps.

	The different layers from the different entities are optionally filtered, buffered and than rasterized.
	Filtering the layers of the files for special attributes enables to further differentiate further.
	For examples makes it possible to differentiate between heath and uncultivated land.
	Adding a buffer can be used either used to convert a line objects as power grids and streets into a polygon with the
	correct physical width, or to add minimum distance from an existing of planed area to the new power grid.
 	Each of theses rasterized layers are given a weight, or cost that expresses the cost of using land covered by this layer.
 	The costs of all layers of is aggregated with the maximum function.
	Thus, an area covered by multiple layers is uniformly used with the highest costs.
	For every area in the study area, that is not covered by any layer, is given the default cost.
	The costs has been grouped into different levels~(see table~\ref{table:1}) starting from preferential areas with
	very low costs, via no restrictions, which is the default, used when no other layers are covering the local area,
	to restricted, strongly restricted and prohibited areas with high costs.
	These higher costs resemble the degree how much a local area should be avoided, while routing the path.
	The ratio of the higher costs to the lower costs directly translates into the additional diversion in pixels
	the algorithm is willing to go, for avoiding an area of high costs.
	Thus, as prohibited areas describe a legal obligation, not to use these areas or only to the utmost minimum,
	the weight that resembles the costs for these types of areas, has to be especially high. \\
	The rasterziation transforms a vector into a raster.
	The rasterization can be executed in to different ways.
	In both ways, the rasterization can be imaged, as the old vector is layered over the new raster grid with the new
	given resolution and the new affine transformation and the coordinate reference system of the vector.
	Both rasterization techniques differ  in who the pixels are selected, that describe, that a geo-object overlays the pixel.
	The pixels can either be described as overlayed with a geo-object, when either the center of that pixel is overlayed
	by the geo-object, or any part of the pixel is overlayed.
	Hence, the version with any part overlayed is called all touched True.
	The version where a overlayed pixel center is require is thus called all touched False.
	All touched False is considered the default (see figure~\ref{fig:alltouched}).
	\begin{figure}[!ht]
		\centering

@@

	\begin{table}[h!]
		\caption{Used levels of costs, the applied numerical equivalent and example layer this cost have been used for.}
		\label{table:1}
		\centering
		\begin{tabular}{ l  r  l }
			Cost Level & Cost &  Example\\
			\hline
			Prohibited & 500					& National Parks, Buildings \\
			strongly Restricted & 10 	& Bird Reserve \\
			Restricted & 5	& Industrial Areas \\
			No Restriction & 0.5					& Default\\
			Preferential & 0.1					& Power Grid, Motorway Buffers\\
		\end{tabular}
	\end{table}
	The completed list of layers and the processing applied to them, can be found in Supplement S1. \todo{create the Supplement from the processing rules}

	\section{Results}
	In this chapter we want to show the different cost raster, that were created from the very same set of layers,
	but computed for different resolutions.
	From this different raster the cost paths are calculated and compared.
	In the last step the raster with lower resolution were used to calculate in a way, that they shall result in
	similar paths as if the paths were computed from a high resolution raster.
	\subsection{Cost Raster}
	\subsection{Least Cost Paths}
	For each resolution the costs paths were estimated for the rasterization with setting all\_touched False
	and all\_touched True.
	The distance of both paths is calculated with the mean minimum distance.
	For every vertex $P_i$ in the path $L_1$ the minimum between the vertex and the path $L_2$
	is computed and afterwards the minimum distances are averaged (see equation~\ref{equ:1}).
	\begin{equation}
		\label{equ:1}
		d_{mean} = \frac{\sum_{i=1}^{n} d_{min}(p_i, L_2)}{n} \bigg\vert p_i \in L_1
	\end{equation}

@@

	\subsection{Faster Processing of the Cost Path Algorithm}
	The original least cost path QGIS plug-in uses stops the least aggregation of the costs after the final end point has been found.
	This early stopping might result in sub optimal paths around the end points.
	For further calculation the search for the least cost paths has to be refactored and split the aggregation of the raster for the search of the path.
	To be able to construct a full aggregated cost raster, aggregated cost path in further steps will be computed completely.\todo{really needed}
	For the calculation of the least cost paths.
	The finally least costs paths should between the least cost paths of the lower resolution, with a tendency to be nearer
	The first step to optimize the calculation speed is, only the calculated the least cost paths for this smaller area. 
	\subsubsection{Apply a minimum sized bounding box around least cost paths}
	\subsubsection{Apply a convex hull round a the last cost paths}
	\subsubsection{Remove unreachable points}

	\section{Discussion}
	\todo{discuss aggregation with max vs sum}
	\section{Related Works}
	\section{Conclusion}

>>>>

	The different layers from the different entities are optionally filtered, buffered and than rasterized.
	Filtering the layers of the files for special attributes enables to further differentiate further.
	For examples makes it possible to differentiate between heath and uncultivated land.
	Adding a buffer can be used either used to convert a line objects as power grids and streets into a polygon with the
	correct physical width, or to add minimum distance from an existing of planed area to the new power grid.
 	Each of theses rasterized layers are given a weight, or cost that expresses the cost of using land covered by this layer.
 	The costs of all layers of is aggregated with the maximum function.
	Thus, an area covered by multiple layers is uniformly used with the highest costs.
	For every area in the study area, that is not covered by any layer, is given the default cost.
	The costs has been grouped into different levels~(see table~\ref{tab:1}) starting from preferential areas with
	very low costs, via no restrictions, which is the default, used when no other layers are covering the local area,
	to restricted, strongly restricted and prohibited areas with high costs.
	These higher costs resemble the degree how much a local area should be avoided, while routing the path.
	The ratio of the higher costs to the lower costs directly translates into the additional diversion in pixels
	the algorithm is willing to go, for avoiding an area of high costs.
	Thus, as prohibited areas describe a legal obligation, not to use these areas or only to the utmost minimum,
	the weight that resembles the costs for these types of areas, has to be especially high. \\
	The rasterization transforms a vector into a raster.
	The rasterization can be executed in to different ways.
	In both ways, the rasterization can be imaged, as the old vector is layered over the new raster grid with the new
	given resolution and the new affine transformation and the coordinate reference system of the vector.
	Both rasterization techniques differ  in who the pixels are selected, that describe, that a geo-object overlays the pixel.
	The pixels can either be described as overlaid with a geo-object, when either the center of that pixel is overlaid
	by the geo-object, or any part of the pixel is overlaid.
	Hence, the version with any part overlaid is called all touched True.
	The version where a overlaid pixel center is require is thus called all touched False.
	All touched False is considered the default (see figure~\ref{fig:alltouched}).
	\begin{figure}[!ht]
		\centering

@@

	\begin{table}[h!]
		\caption{Used levels of costs, the applied numerical equivalent and example layer this cost have been used for.}
		\label{tab:1}
		\centering
		\begin{tabular}{ l  r  l }
			Cost Level & Cost &  Example\\
			\hline
			Prohibited & 500					& National Parks, Buildings \\
			strongly Restricted & 10 	& Bird Reserve \\
			Restricted & 5	& Industrial Areas \\
			No Restriction & 0.5					& Default\\
			Preferential & 0.1					& Power Grid, Motorway Buffers\\
		\end{tabular}
	\end{table}
	The completed list of layers and the processing applied to them, can be found in Supplement S1. \todo{create the Supplement from the processing rules}

	\section{Results}
	In this chapter we want to show the different cost raster, that were created from the very same set of layers,
	but computed for different resolutions.
	From this different raster the cost paths are calculated and compared.
	In the last step the raster with lower resolution were used to calculate in a way, that they shall result in
	similar paths as if the paths were computed from a high resolution raster.
	\subsection{Cost Raster}
	\subsection{Least Cost Paths}
	For each resolution the costs paths were estimated for the rasterization with setting all\_touched False
	and all\_touched True.
	The distance of both paths is calculated with the mean minimum distance.
	For every vertex $P_i$ in the path $L_1$ the minimum between the vertex and the path $L_2$
	is computed and afterwards the minimum distances are averaged (see equation~\ref{eq:1}).
	\begin{equation}
		\label{eq:1}
		d_{mean} = \frac{\sum_{i=1}^{n} d_{min}(p_i, L_2)}{n} \bigg\vert p_i \in L_1
	\end{equation}

@@

	\subsection{Faster Processing of the Cost Path Algorithm}
	The original least cost path QGIS plug-in uses stops the least aggregation of the costs after the final end point has been found.
	This early stopping might result in sub optimal paths around the end points.
	For further calculation the search for the least cost paths has to be refactored and split the aggregation of the raster for the search of the path.
	To be able to construct a full aggregated cost raster, aggregated cost path in further steps will be computed completely.\todo{really needed}
	For the calculation of the least cost paths.
	The finally least costs paths should between the least cost paths of the lower resolution, with a tendency to be nearer
	The first step to optimize the calculation speed is, only the calculated the least cost paths for this smaller area. 
	\subsubsection{Compare least cost paths, for overlay of both rasterizations}
	\subsubsection{Restrict search to a minimum sized bounding box}
	\subsubsection{Restrict search to a convex hull}
	\subsubsection{Restrict search to reachable points}

	\subsubsection{Compare the different Solutions}
	\subsubsection{Check solution for least cost path between different points}

	\section{Discussion}
	\todo{discuss aggregation with max vs sum}
	\todo{discuss other methods. Off algorithmic speed-ups}
	\todo{discuss other technical methods of speed-ups, as precompilation, JIT, vector units, multi-core}
	\section{Related Works}
	\section{Conclusion}
